New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-03-12 main.tex
Created a 'Contributions' section with the main points we want to discuss in the paper

>>>>

\subsection{Novel Contributions}

The study and results presented in this article lead to two main contributions:
new insights on the impact of the cognitive context of the interaction on the
perception of a robot by humans; a novel unbiased\fxwarning{correct?}
methodology based on eye-tracking to measure anthropomorphic attributions during
a running human-robot interaction.

Our first contribution extends our understanding of the attribution of
human-like characteristics to robot by exploring the role of the interaction
context. As we will show in the article, it appears that \textbf{even relatively
subtle context priming may lead to significantly different anthropomorphic
perceptions of the exact same robot, performing the exact same task}, as
confirmed both by distinct gaze patterns, and different reported perceptions in
questionnaires. As far as we know, this effect had not been previously
evidenced.

This leads to a second-order effect that we also evidence here: depending on the
cognitive context, the tendency to attribute human-like characteristics to robot
\textbf{evolves} in significantly different ways: after observing a robot in a
context that pre-suppose deeper cognitive capabilities, \textbf{people increase
their general tendency to anthropomorphize robots} compared to a shallow
cognitive context, even though the robot appearance and behaviour is the exact
same.

The second contribution is a methodological one: we present in this article
\textbf{a novel technique to assess anthropomorphic projections that relies on a
biometric measurement (eye-tracking) to compare gaze fixation durations on
the face of the robot}. We cross-validate this new metric with existing,
established, questionnaires. Compared to current techniques (post-hoc
annotations of videos and questionnaires), this new approach is objective,
is less impacted by experimental biases (like the \emph{observer effect},
where the subject's behaviour is impacted by the fact he/she knows that
he/she is observed) and take place during the interaction itself
(\emph{in-the-moment} measurement).

Besides, we also introduce a new kind of visual stimuli, specifically designed
to study the impact of non-appearance, non-behavioural related effects on the
human-like perception of robots. We make these video stimuli available to the
community, and therefore invite our colleagues to reproduce our experimental
results.

As a whole, we believe that this article provide a solid contribution, both in
terms of methodology and experimental evidence, to our understanding of one of
the intricate psychological effects that come to play when humans and robots
interact.
